Combine_results

### 2017-02-21 Code/combine_results.Rmd

```{r combine_results}
age_cod_results <- read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/age_cod_set_1.csv")
age_decomp_results <- read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/age_decomp_set_1.csv")
BlackWhite_results <- read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/BlackWhite_set_1.csv")
cod_decomp_results <- read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/cod_marginal_set_1.csv")

for(i in 2:8){
  age_cod_results <- rbind(age_cod_results, 
                           read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/age_cod_set_",
                                           i, ".csv")))
  age_decomp_results <- rbind(age_decomp_results, 
                              read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/age_decomp_set_",
                                              i, ".csv")))
  BlackWhite_results <- rbind(BlackWhite_results, 
                              read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/BlackWhite_set_",
                                              i, ".csv")))
  cod_decomp_results <- rbind(cod_decomp_results, 
                              read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/cod_marginal_set_",
                                              i, ".csv")))
}
```

@@

```{r save_combined_datasets, echo = F}
write.csv(age_cod_results, "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/age_cod_results.csv")
write.csv(age_decomp_results, "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/age_decomp_results.csv")
write.csv(cod_decomp_results, "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/cod_decomp_results.csv")
write.csv(BlackWhite_results, "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/BlackWhite_results.csv")
```

>>>>

```{r}
included.states <- c("Alabama", "Arizona", "Arkansas", "California", "Colorado", "Connecticut",
"Delaware", "Florida", "Georgia", "Illinois", "Indiana", "Iowa", "Kansas", "Kentucky",
"Louisiana", "Maryland", "Massachusetts", "Michigan", "Minnesota", "Mississippi",   
"Missouri", "Nebraska", "Nevada", "New Jersey", "New Mexico", "New York",
"North Carolina", "Ohio", "Oklahoma", "Oregon", "Pennsylvania", "Rhode Island",
"South Carolina",  "Tennessee", "Texas", "Virginia", "Washington", "Washington DC",
"West Virginia", "Wisconsin")

completed.states <- included.states[17:24]
```

```{r combine_results}
age_cod_results <- read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/age_cod_", completed.states[1], ".csv"))
age_decomp_results <- read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/age_decomp_", completed.states[1], ".csv"))
BlackWhite_results <- read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/BlackWhite_", completed.states[1], ".csv"))
cod_decomp_results <- read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/cod_marginal_", completed.states[1], ".csv"))
cod_change_results <- read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/cod_change_", completed.states[1], ".csv"))

mortality.rates <- read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/mortality_rates_", completed.states[1], ".csv"))
mortality.rates.diff <- read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/mortality_rates_diff_", completed.states[1], ".csv"))

for(state_i in 1:length(completed.states)){

    age_cod_results <- rbind(age_cod_results, read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/age_cod_", completed.states[state_i], ".csv")))

    age_decomp_results <- rbind(age_decomp_results, read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/age_decomp_", completed.states[state_i], ".csv")))

    BlackWhite_results <- rbind(BlackWhite_results, read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/BlackWhite_", completed.states[state_i], ".csv")))

    cod_decomp_results <- rbind(cod_decomp_results, read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/cod_marginal_", completed.states[state_i], ".csv")))

    cod_change_results <- rbind(cod_change_results, read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/cod_change_", completed.states[state_i], ".csv")))

  mortality.rates <- rbind(mortality.rates, read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/mortality_rates_", completed.states[state_i], ".csv")))

    mortality.rates.diff <- rbind(mortality.rates.diff, read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/mortality_rates_diff_", completed.states[state_i], ".csv")))
}

mortality.rates <- mortality.rates %>% mutate(state.reorder = reorder(state, as.numeric(Census_Division)))
mortality.rates.diff <- mortality.rates.diff %>% mutate(state.reorder = reorder(state, as.numeric(Census_Division)))
```

@@

```{r save_combined_datasets, echo = F}
write.csv(age_cod_results, "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/age_cod_results.csv")
write.csv(age_decomp_results, "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/age_decomp_results.csv")
write.csv(cod_decomp_results, "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/cod_decomp_results.csv")
write.csv(BlackWhite_results, "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/BlackWhite_results.csv")

write.csv(mortality.rates, "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/mortality_rates_combined.csv")
write.csv(mortality.rates.diff, "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/mortality_rates_diff_combined.csv")
```
